\documentclass[a4paper,10pt]{article}
\usepackage[left=0.5in,right=0.5in,top=0.5in,bottom=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{6pt}{4pt}

\setlist[itemize]{leftmargin=*,nosep,topsep=2pt}

\pagenumbering{gobble}

\begin{document}

\begin{center}
    {\LARGE \textbf{Abdelrahman Ahmed Hassan Atia}}\\[4pt]
    Egypt, Giza, 6 October\\[2pt]
    \href{mailto:abd.ahmed.hass@gmail.com}{abd.ahmed.hass@gmail.com} $|$ 
    +20 01145771230 $|$ 
    \href{https://github.com/Abdelrahman730}{GitHub: Abdelrahman730} $|$ 
    Military Status: Exempted
\end{center}

\vspace{-8pt}

\section*{Professional Summary}
Results-driven Backend Engineer with a strong foundation in software engineering, DevOps, and machine learning. Expert in architecting scalable server-side systems, designing robust APIs, and optimizing database performance. Skilled in containerization (Docker, Kubernetes), CI/CD pipelines, and cloud orchestration. Passionate about building high-availability infrastructure, automated production systems, and deriving performance insights from complex backend architectures.

\vspace{-4pt}

\section*{Education}
\textbf{Bachelor of Information Technology and Computer Science} \hfill 2019 -- 2023\\
Nile University, Giza, Sheikh Zayed\\
Concentration: Media Informatics $|$ GPA: 3.69/4.0

\vspace{-4pt}

\section*{Technical Expertise}
\textbf{Backend \& Core:} Node.js, PHP, C++, C, Python, API Architecture, Server-Side Logic, Algorithm Design\\
\textbf{Infrastructure (DevOps):} Docker, Kubernetes, Jenkins, CI/CD Pipelines, Git, Linux, Bash Shell Scripting\\
\textbf{Web Development:} React.js, HTML5, CSS3, JavaScript (ES6+), Full-Stack Systems\\
\textbf{Machine Learning \& AI:} Deep Learning, TensorFlow Lite, Computer Vision, OpenCV, Reinforcement Learning\\
\textbf{Databases:} MySQL, Database Design \& Query Optimization\\
\textbf{Tools \& Frameworks:} Android Studio, ImGUI, Dear ImGui, Vulkan SDK

\vspace{-4pt}

\section*{Professional Experience}
\textbf{Teaching Assistant, Computer Science Department} \hfill Oct 2025 -- Present\\
German University in Cairo (GUC), Cairo
\begin{itemize}
    \item Mentoring 200+ undergraduate students in Advanced Programming, Data Structures, and Software Engineering.
    \item Conducting technical lab sessions, directing code reviews, and assisting with complex debugging in C++ and Python.
    \item Bridging the gap between theoretical computer science and production-ready implementation practices.
\end{itemize}

\vspace{2pt}

\textbf{Junior Teaching Assistant, Computer Science Department} \hfill Oct 2020 -- Feb 2021\\
Nile University, Giza
\begin{itemize}
    \item Supported core programming courses and mentored students on semester-long software development projects.
    \item Facilitated technical queries, assisted with code reviews, and managed lab debugging sessions.
\end{itemize}

\vspace{-4pt}

\section*{Key Projects}
\textbf{DevOps Web Deployment & Pipeline Orchestration} \hfill Nov 2025\\
Infrastructure Practice Project
\begin{itemize}
    \item Engineered a containerized deployment environment using Docker for a distributed web application.
    \item Implemented an automated CI/CD pipeline with Jenkins for continuous testing and staging deployment.
    \item Orchestrated production-ready services using Kubernetes clusters and multi-stage Docker builds.
\end{itemize}

\vspace{2pt}

\textbf{ASSIST ME: Mobile Vision System for Visually Impaired} \hfill June 2023\\
Graduation Project -- Computer Vision \& Deep Learning
\begin{itemize}
    \item Developed a life-assist mobile application featuring reading and navigation modules using OCR and YOLOv8.
    \item Engineered optimized TensorFlow Lite models for mobile deployment, achieving 95\% text recognition accuracy.
    \item Integrated roadmap sign recognition, CNN-based facial recognition, and ToF sensor-based distance estimation.
\end{itemize}

\vspace{2pt}

\textbf{Interactive Parse Tree Visualizer (Backend Focus)} \hfill June 2023\\
C++ Logic & Graphics System (Vulkan & ImGUI)
\begin{itemize}
    \item Engineered a high-performance backend for real-time code tokenization and AST generation.
    \item Developed an interactive graph rendering engine using Vulkan for low-latency node-based visualization.
\end{itemize}

\vspace{2pt}

\textbf{Regex-to-Finite-Automaton Converter} \hfill June 2022\\
C++ Logic Engine & ImGUI UI
\begin{itemize}
    \item Developed a robust engine to transpile regular expressions into deterministic and non-deterministic finite automata.
    \item Implemented graph-based rendering and state transition animations focusing on algorithmic accuracy.
\end{itemize}

\vspace{2pt}

\textbf{Restaurant Management System (Backend-First)} \hfill June 2022\\
Full-Stack Web App (React.js, Node.js, MySQL)
\begin{itemize}
    \item Built a comprehensive order and inventory management system with secure analytical dashboards.
    \item Designed a relational database schema and role-based access control (RBAC) for secure operation.
\end{itemize}

\vspace{2pt}

\textbf{Automated University Management System} \hfill Jan 2022\\
Web Application (PHP, MySQL, HTML, CSS, JS)
\begin{itemize}
    \item Created a full-featured academic portal for students, faculty, and admins with role-based authentication.
    \item Managed complex student registration, grading, and attendance logic with optimized SQL data handling.
\end{itemize}

\vspace{-4pt}

\section*{Professional Certifications}
\textbf{KodeKloud:} Docker for Beginners, Kubernetes for Beginners, Jenkins for Beginners\\
\textbf{IBM:} Data Science Specialization (Nov 2022), Data Analysis Specialization (Oct 2022)\\
\textbf{Meta:} Version Control (Sept 2022), iOS Development (Sept 2022)

\vspace{-4pt}

\section*{Languages}
Arabic: Native $|$ English: Professional Working Proficiency

\end{document}
